---
title: "Template Document"
author:
- name: Kieran Healy
  affiliation: Duke University
  email: kieran.healy@duke.edu
date: '`r format(Sys.Date(), "%B %d, %Y")`'
crossrefYaml: "config/pandoc-crossref-settings.yaml"
output:
  bookdown::pdf_book: 
    toc: false
    md_extensions: +simple_tables+table_captions+yaml_metadata_block+smart
    template: /Users/kjhealy/.pandoc/templates/rmd-latex.template
    pandoc_args: [
      "--bibliography", "/Users/kjhealy/Documents/bibs/socbib-pandoc.bib",
      "--citeproc",
      "--csl", "/Users/kjhealy/.pandoc/csl/ajps.csl"
      ]      
  html_document: 
  md_document: 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
                      fig.path='figures/',
                      cache.path='cache/',
                      dev=c("ragg_png","cairo_pdf"),
                      fig.width = 6,
                      fig.asp = 0.7,
                      fig.retina = 2,
                      fig.show='hold',
                      fig.lp="fig:",
                      fig.pos = "t",
                      fig.align = "center",
                      dpi = if (knitr::is_latex_output()) 72 else 300,
                      cache=FALSE,
                      par=TRUE,
                      echo=FALSE,
                      warning = FALSE,
                      results="asis",
                      message=FALSE)

knitr::knit_hooks$set(par = function(before, options, envir){
    if (before && options$fig.show != 'none') par(mar = c(4,4,.1,.1), cex.lab = .95, cex.axis = .9, mgp = c(2, .7, 0), tcl = -.3)
}, crop=knitr::hook_pdfcrop)

knitr::opts_knit$set(kfigr.prefix=TRUE,
              kfigr.link=FALSE)

```

```{r libraries}

library(tidyverse)
library(here)
library(janitor)
library(socviz)
library(ggrepel)

library(systemfonts)
clear_registry()

register_variant(
  name = "Myriad Pro SemiCondensed",
  family = "Myriad Pro",
  width = "semicondensed",
  weight = c("normal", "semibold"),
)

library(showtext)
showtext_opts(dpi = 300)
showtext_auto()

library(myriad)
import_myriad_semi()


theme_set(theme_myriad_semi())

```

# Introduction

This is a template for `Rmd` documents. 

`r stringi::stri_rand_lipsum(1, start_lipsum = TRUE)`

# Data

`r stringi::stri_rand_lipsum(1, start_lipsum = TRUE)`

Here is a code chunk.

```{r rawmt, results='markup', echo=TRUE}
tibble(mtcars)
```

`r stringi::stri_rand_lipsum(3, start_lipsum = TRUE)` 

Or as a table:

```{r mtcars, echo=FALSE}
knitr::kable(mtcars[1:5, 1:5], caption = "The mtcars data.", format = "pipe")
```

`r stringi::stri_rand_lipsum(1, start_lipsum = TRUE)`

# Analysis

We show a figure in Figure \@ref(fig:mpg-disp).

Also see Equation \@ref(eq:mean).

\begin{equation}
\bar{X} = \frac{\sum_{i=1}^n X_i}{n} (\#eq:mean)
\end{equation}

And see Table \@ref(tab:mtcars).



`r stringi::stri_rand_lipsum(1, start_lipsum = TRUE)`

```{r mpg-disp, fig.cap="An mtcars plot."}
mtcars |>
  ggplot(mapping = aes(x = disp,
                       y = mpg)) +
  geom_point() + 
  geom_smooth(se = FALSE) + 
  labs(title = "Fuel efficency and engine displacement", 
       xlab = "Displacement", 
       ylab = "Miles per Gallon")
```



